Predicting _C. difficile_ Infection Severity from the Taxonomic Composition of the Gut Microbiome

### 2023-05-18 paper/paper.qmd
Add relative abundance to feature importance plot

::: {#fig-features fig-cap="**Feature importance.**
Feature importance via permutation test.
For each OTU, the order of samples was randomized in the test set 100 times and
the performance was re-calculated to estimate the permutation performance.
An OTU was considered important if the performance decreased when the OTU was
permuted in at least 75% of the models.
OTUs with a greater difference in AUROC (actual performance minus permutation
performance) are more important.
Left: models were trained on the full dataset, with different numbers of samples
available for each severity definition.
Right: models were trained on the intersection of samples with all labels
available for each definition. Note that Attributable and Pragmatic severity are
exactly the same for the intersection set.
OTU 120 (*Pseudomonas*) is not shown for the full data set with IDSA severity 
on the full dataset because it was removed during pre-processing due to having
near-zero variance.
"}
![](figures/feature-importance.png)
:::

>>>>

::: {#fig-features fig-cap="**Feature importance.**
**A)** Feature importance via permutation test.
For each OTU, the order of samples was randomized in the test set 100 times and
the performance was re-calculated to estimate the permutation performance.
An OTU was considered important if the performance decreased when the OTU was
permuted in at least 75% of the models.
OTUs with a greater difference in AUROC (actual performance minus permutation
performance) are more important.
Left: models were trained on the full datasets, with different numbers of
samples available for each severity definition.
Right: models were trained on the intersection of samples with all labels
available for each definition. Note that Attributable and Pragmatic severity are
exactly the same for the intersection set.
OTU 120 (*Pseudomonas*) is not shown for the full data set with IDSA severity 
on the full dataset because it was removed during pre-processing due to having
near-zero variance.
**B)** Log~10~ transformed median relative abundances of the most important OTUs
on the full datasets, grouped by severity (shape).
"}
![](figures/feature-importance.png)
:::
